---
title: "My First Project"
author: "Cephas Dube"
date: "19 September 2016"
output: word_document
---
# Loading the necessary packages to compile Project
```{r}
library(dplyr)
library(readr)
library(tidyr)
library(lubridate)
library(knitr)
library(ggplot2)
library(dplyr)
```



# Getting Raw Data into Project
```{r}
eqs_file <- list.files(path = "G:/Cephas/Rproject/Files.csv", full.names = TRUE) %>% lapply(read.csv) %>% bind_rows()



```

# Getting the 20 largest MarketCapUSD stocks(LMC)

```{r}

LMC <- eqs_file %>% group_by(date) %>% select(Ticker, MarketCapUSD) %>% arrange(desc(MarketCapUSD)) %>% slice(1:20) %>% ungroup()


```

# Displaying columns in a table ranked by MarketCapUSD

```{r}
F_month <- eqs_file %>% filter(date == ymd("2016-01-31")) %>% select(date,Ticker, MarketCapUSD) %>% arrange(desc(MarketCapUSD))

T_1 <- kable(F_month, results='asis')

```

# Creating dataframe with Z-score for the BookYield column for the first month

```{r}
Z_BYield <- eqs_file %>% filter(date == ymd("2016-01-31")) %>% mutate(BookYield_z = (BookYield-mean(BookYield, na.rm = TRUE))/sd(BookYield, na.rm = TRUE)) %>% select(date, Ticker,BookYield_z)

T_2 <- kable(Z_BYield, digits = 2, results = 'asis')

```

# Calculating Z-score for the BookYield column for every month

```{r}

Z_BY <- eqs_file %>% group_by(date) %>% mutate(BYZ = (BookYield-mean(BookYield, na.rm = TRUE))/sd(BookYield, na.rm = TRUE)) %>% ungroup()

```

# Getting 10 stocks with highest BookYield Z-Score in each month

```{r}
HBY_z <- Z_BY %>% group_by(date) %>% arrange(desc(BYZ)) %>% slice(1:10) %>% ungroup()

```

# Calculating the Market Cap Weighted weight for the 10 stocks above

```{r}
MktCap_weighted <- HBY_z %>% group_by(date) %>% mutate(MCap_weighted = (MarketCapUSD)/sum(MarketCapUSD, na.rm = TRUE)) %>% ungroup()

```

# Calculating the EarningsYield for the Cap-Weighted portfolio

```{r}

EY_P <- MktCap_weighted %>% group_by(date) %>% summarise(EYield_p =sum(EarningsYield * MCap_weighted, na.rm = TRUE)) %>% ungroup()
                                              
T_3 <- kable(EY_P, digits = 2,results = 'asis')

```

# Plotting bar chart for BYZ

```{r}

BarChart <- Z_BY %>% group_by(date) %>% filter(date == ymd("2016-01-31")) %>% select(Ticker,BYZ) %>% ggplot(mapping = aes(x = Ticker, y = BYZ)) + geom_bar(stat = "identity", width = 2) + coord_flip()
```

# Plotting timeseries of Cap Weighted Portfolio EarningsYield

```{r}
CapWeighted_P <- ggplot(data = EY_P) + geom_line(mapping = aes(x = date, y = EYield_p, group = 1))

```
